Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
Benchmarks description

A set of state-space models for different classes of 
systems were extracted from the 
literature~\cite{Franklin15,maglev,converters,CTMS} 
and employed for validating our methodology. 
%All systems are SISO models of the following form:
%
%\begin{equation}
%\left\lbrace\begin{array}{c}
%\dot{\textbf{x}}(t)=\textbf{A}\textbf{x}(t)+\textbf{B}u(t)\\
%y(t)=\textbf{C}\textbf{x}(t)+\textbf{D}u(t)
%\end{array}\right.
%\end{equation}
%
Table~\ref{table:State-space benchmarks} summarizes 
all our benchmarks, which are SISO models (cf. section~\ref{sec:preliminaries}). 
\todo{they are not: we do not have a 1d output map (SO= single output), rather get access to all variables. so the output map (C) is the identity, if you will. 
this is a good point to clarify this, mention possible extensions to observer-based feedback architectures. }

>>>>

A set of state-space models for different classes of 
systems were extracted from the 
literature~\cite{Franklin15,maglev,converters,CTMS} 
and employed for validating our methodology. 
%All systems are SISO models of the following form:
%
%\begin{equation}
%\left\lbrace\begin{array}{c}
%\dot{\textbf{x}}(t)=\textbf{A}\textbf{x}(t)+\textbf{B}u(t)\\
%y(t)=\textbf{C}\textbf{x}(t)+\textbf{D}u(t)
%\end{array}\right.
%\end{equation}
%
Table~\ref{table:State-space benchmarks} summarizes 
all our benchmarks, which are SISO models (cf. section~\ref{sec:preliminaries}). In the Table~\ref{table:State-space benchmarks}, the Inverted Pendulum appears to be a two output system but it was treated as two SISO systems during the experiments. For the sake of simplicity all the states measurements are assumed available. In practice, state estimators should be designed in order to obtain an estimate of the states from the single output. Further extensions of this work can include state observers synthesis.

%\todo{they are not: we do not have a 1d output map (SO= single output), rather get access to all variables. so the output map (C) is the identity, if you will. 
%this is a good point to clarify this, mention possible extensions to observer-based feedback architectures. }
